---
title: "Airbnb-Boulder-EDA"
output: pdf_document
date: "2023-12-13"
---

# Intro
This analysis looks at the ***** 80301 Zipcode of Unincorporated Boulder County. Nevertheless, this is moduraliized to fit whatever city or area. 

## Libraries 
```{r include=FALSE}
library('tidyverse')
```

## Import Data
This notebook incorporates a few different sites to perform a better model 

https://www.airbnb.com/host/homes?src_section=342893&c=.pi80.pkb21uaS80LzU3OTYw&euid=3d724216-eaba-8ba5-dd4f-8f01752d073b&room_type=ENTIRE_HOME

https://app.airdna.co/data/us/59323?tab=performance

### Information based on Equivalent property. 
  -equivalent property == 1-2 bedroom, independent, whole unit

## Occupancy Dataframe

TODO: determine if occupancy is necessary to include; if so... 
TODO: separate into an object in an instance (driver code)

Thus,a seasonal trend line has been encoded to scale between 50% and 80% weighted based on the season. The price is adjusted as well between 120 and 170.  . 
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

# Define the income parameters
occupancy_rate_low_season <- 0.5
occupancy_rate_high_season <- 0.8  
nightly_rate_low_season <- 120
nightly_rate_high_season <- 170 
months <- 1:12
days_in_month <- c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)

# Create a data frame to store the results
result_df <- data.frame(Month = integer(), Revenue = numeric())
```

## Revenue Data

Here, a revenue class weights attributes  
  1. high season 
  2. low season 
  3. transitional seasons linking the two.

```{r Revenue}
# Define Revenue class
Revenue <- setClass(
  "Revenue",
  slots = list(
    nightly_rate_high_season = "numeric",
    nightly_rate_low_season = "numeric",
    occupancy_rate_high_season = "numeric",
    occupancy_rate_low_season = "numeric",
    days_in_month = "list"
  )
)

# Function to calculate monthly revenue
calculateMonthlyRevenue <- function(month, revenueObj) {
  days <- revenueObj@days_in_month[[month]]
  nightlyRate <- ifelse(month %in% c(6, 7, 8, 9), revenueObj@nightly_rate_high_season, revenueObj@nightly_rate_low_season)
  occupancyRate <- ifelse(month %in% c(12, 1, 2), revenueObj@occupancy_rate_low_season, revenueObj@occupancy_rate_high_season)
  revenue <- occupancyRate * nightlyRate * days
  return(revenue)
}

```

### Instance
```{r}
#Instnace usage for revenue
localRevenue <- Revenue(
  nightly_rate_high_season = 150,
  nightly_rate_low_season = 100,
  occupancy_rate_high_season = 0.8,
  occupancy_rate_low_season = 0.6,
  days_in_month = list(January = 31, February = 28, March = 31, April = 30, May = 31, June = 30, 
                       July = 31, August = 31, September = 30, October = 31, November = 30, December = 31)
)

# Initialize an empty tibble
result_df <- tibble::tibble(Month = character(), Revenue = numeric())

# Calculate revenue for each month
for (month in names(localRevenue@days_in_month)) {
  revenue <- calculateMonthlyRevenue(month, localRevenue)
  result_df <- tibble::add_row(result_df, Month = month, Revenue = revenue)
}

# Display the result_df tibble
result_df
```

## Expense Data 

Here, an Expense class weights attributes  
  1. fee of management company. 
  2. business expense
  3. misc expenses 
```{r}
# Define Expenses class; Refacotr where misc_expenses = "list"
Expenses <- setClass(
  "Expenses",
  slots = list(
    management_expenses = "numeric",
    airbnb_fee = "numeric"
  )
)

# Function to calculate total expenses
calculateTotalExpenses <- function(revenue, expensesObj) {
  managementExpenses <- revenue * expensesObj@management_expenses
  miscExpenses <- sum(unlist(expensesObj@misc_expenses))
  totalExpenses <- managementExpenses + miscExpenses
  return(totalExpenses)
}
```
### Instance
```{r}
# Example usage for short-term rental
localExpenses <- Expenses(
  management_expenses = 0.82,
  airbnb_fee = 0.00
  #misc_expenses = list(Food = 1000, Appliances = 100, Gas = 10)
)

```


## Income Data 

Function of the two previous functions. 

TODO: Still has to be transformed.

```{r}
# Function to calculate rental revenue
calculateRentalRevenue <- function(dailyRate, numberOfDays) {
  revenue <- dailyRate * numberOfDays
  return(revenue)
}

# Function to calculate rental expenses
calculateRentalExpenses <- function(costPerDay, numberOfDays) {
  expenses <- costPerDay * numberOfDays
  return(expenses)
}

# Function to calculate rental income
calculateRentalIncome <- function(revenue, expenses) {
  income <- revenue - expenses
  return(income)
}
```

## Including Plots
```{r Plots, echo=FALSE}
ggplot(result_df, aes(x = Month, y = Revenue)) +
  geom_line() +
  labs(title = 'Monthly Revenue Based on Seasonal Occupancy and Nightly Rates',
       x = 'Month',
       y = 'Revenue') +
  theme_minimal() +
  scale_x_discrete(labels = month.name)
```

## Footnote:

-Due to limitations of available and reliable data, incomplete comparisons, and other confounders this representation will be incomplete, yet will still serve as a template to make future decisions with similar circumstances. 

# Reminder 

Utilize this model as leverage for pricing, since its something which can be done in an automated way. Thus, Shannon's time may be nulled by some executable scripts. The only caveat is I need her info/data. 